X-Factors: External Influences of a Hockey Goaltender's Performance

### 2024-12-04 paper/paper.qmd
fixing reference format

To analyze the effect of external factors on goaltender performance, we use a log of 394,250 shots taken during the 2021-22 to 2024-25 NHL regular and post-seasons, provided by Moneypuck [@data]. These are split by season and titled *2021-2022 Season (121,471 Shots)*, *2022-2023 Season (122,026 Shots)*, *2023-2024 Season (122,472 Shots)*, and *2024-2025 Season (33,648 shots)"*. Moneypuck is a publicly available source of hockey analytics that tracks advanced statistics, playoff odds, and event data. The shot data is updated daily from official NHL game reports. For the current 2024-25 season, data is included up to November 26, 2024.

>>>>

To analyze the effect of external factors on goaltender performance, we use a log of 394,250 shots taken during the 2021-22 to 2024-25 NHL regular and post-seasons, provided by MoneyPuck [@data]. These are split by season and titled *2021-2022 Season (121,471 Shots)*, *2022-2023 Season (122,026 Shots)*, *2023-2024 Season (122,472 Shots)*, and *2024-2025 Season (33,648 shots)"*. Moneypuck is a publicly available source of hockey analytics that tracks advanced statistics, playoff odds, and event data. The shot data is updated daily from official NHL game reports. For the current 2024-25 season, data is included up to November 26, 2024.
